\textsc{TheHaloMod}: An online calculator for the halo model

### 2020-09-29 paper.tex
Updates from Overleaf
ZC added acknowledgement
Put citation_fix into main text

\input{citation_fix}

@@

\section*{Acknowledgements}
SGM acknowledges many useful discussions with colleagues that formed the basis of this paper, including Chris Power, Aaron Robotham, Chris Blake, Florian Beutler and David Palomara. 
All figures in this paper were produced with \textsc{matplotlib} \citep{Hunter2007}. We acknowledge the extremely helpful \textsc{numpy} \citep{vanderWalt2011}, \textsc{astropy} \citep{Robitaille2013,AstropyCollaboration2018} and \textsc{SciPy} \citep{Virtanen2020} codes.

>>>>

\usepackage{etoolbox}
\makeatletter
% Patch case where name and year have no delimiter
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{\NAT@nmfmt{\NAT@nm}\NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}\NAT@hyper@{\NAT@date}}
  {}% Do nothing if patch works
  {}% Do nothing if patch fails
% Patch case where name and year have basic delimiter
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar%
   \NAT@hyper@{\NAT@date}}
  {}% Do nothing if patch works
  {}% Do nothing if patch fails
% Patch case where name and year are separated by a prenote
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi%
   \NAT@hyper@{\NAT@date}}
  {}% Do nothing if patch works
  {}% Do nothing if patch fails
\makeatother

@@

\section*{Acknowledgements}
SGM acknowledges many useful discussions with colleagues that formed the basis of this paper, including Chris Power, Aaron Robotham, Chris Blake, Florian Beutler and David Palomara. 
ZC acknowledges support from the Overseas Research Scholar Awards from the School of Physics and Astronomy, The University of Manchester.
All figures in this paper were produced with \textsc{matplotlib} \citep{Hunter2007}. We acknowledge the extremely helpful \textsc{numpy} \citep{vanderWalt2011}, \textsc{astropy} \citep{Robitaille2013,AstropyCollaboration2018} and \textsc{SciPy} \citep{Virtanen2020} codes.
